 \documentclass[a4paper]{article}

\usepackage{parskip}
\usepackage{url}
\usepackage{multicol}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{tabularx}

\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault}
\usepackage[T1]{fontenc}


\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{3pt}{3pt} % Spacing around sections

\begin{document}
\pagestyle{empty} % Removes page numbering
%---------------------------------
%	NAME AND CONTACT INFORMATION
%---------------------------------
\begin{multicols}{2}

\raggedright{\textsc{\Huge{James Campbell}}}\\
\columnbreak
\raggedleft{
3 Hillside Close, Helsby\\
Cheshire, UK, WA6 9LB \\
+44 7876 075714\\
\href{mailto:james.campbell@tanti.org.uk}{james.campbell@tanti.org.uk}}

\end{multicols}
%----------------------
%   PERSONAL PROFILE
%----------------------
\section{Personal Profile/Objective}
I am an undergraduate with a mature outlook seeking a year long industrial placement aiming to put my advanced knowledge of mathematics and computer science in practice.
I have a logical mind and demonstrated my ability to understand complex ideas quickly whilst working on a research project at Cardiff University when I was chosen out of 160 of my peers to undertake a research internship (Summer 2013-2014).
I am an excellent communicator and am comfortable speaking in front of large groups, which I showed when I presented my work at an International Conference (March 2013-2014).

%--------------------
%	WORK EXPERIENCE
%--------------------
\section{Experience}
\begin{tabularx}{\textwidth}{lX}

\textsc{Summer} & Building Game Theoretical Software in a Research Environment \\
\textsc{2014}& \footnotesize{I was employed by Cardiff University Department of Mathematics, working with Dr. Vincent Knight to \textbf{lead} the department's contribution to the open source mathematics package, Sage (an open source Mathematics software package).
I was \textbf{responsible} for the implementation of a variety of Game Theoretic algorithms that will be included in a future release of Sage.
Areas of Game Theory included: Normal Form Games, Co-operative Games and Matching Games.
This employment developed my \textbf{teamwork} and \textbf{communication} skills by providing experience of working within a research environment with \textbf{international} collaborators.}\\
\\

\textsc{Spring Semester} & Experiencing Mathematics within an Entrepreneurial Environment\\
\textsc{2014}& \footnotesize{In the scope of the Computing for Mathematics module three of my peers and I formed a role playing company (11 week assessed activity).
My role within this company was the \textbf{development} of a dynamic website using the web development framework Django.
In a \textbf{short amount of time} I gained the necessary skills to build a dynamic and professional website.
Throughout this I routinely \textbf{communicated} complex ideas to my peers as well as gaining skills in \textbf{business strategy}, \textbf{idea generation} and \textbf{project management}.
}\\
\\
%------------------------------------------------
\textsc{Sept 2010 -} & Referee with the Rugby Football Union \\
\textsc{Present} & \footnotesize{Whilst most teenagers might have a Saturday job, I began refereeing rugby union at the age of 15.
New referees start at level 15 and within 3 years, I had been \textbf{promoted} to level 6 - the \textbf{highest} regional level and only one below the point where I could referee national level games.
The experience of \textbf{taking charge} of 30 men (often twice my age) in an aggressive and physical sport has given me confidence in my ability to \textbf{remain calm in stressful situations}.}\\
\\
%------------------------------------------------
\textsc{Sept 2009 -} & Young Leader at 1\textsuperscript{st} Helsby Scouts\\
\textsc{Jul 2013}& \footnotesize{I developed communication skills whilst helping to supervise and teach children aged 6 - 10 years.
I was regularly assigned to lead small group activities which improved my organisation and leadership skills.}\\

\end{tabularx}
%--------------
%	EDUCATION
%--------------
\section{Education}
\begin{tabularx}{\textwidth}{lX}

\textsc{Current} & \textsc BSc Mathematics, Statistics and Operational Research \\
&\normalsize Cardiff University, Department of Mathematics\\
& Expected May 2017\\
\\
%------------------------------------------------
\textsc{Sept 2011 -} & St. Nicholas Catholic High School\\
\textsc{June 2013} & A-Levels: Maths - A*, Further Maths - A, Physics - A\\
& AS-Levels: Biology - B, Chemistry - B\\
\\
%------------------------------------------------
\textsc{Sept 2006 -} & St. Nicholas Catholic High School\\
\textsc{June 2011} & GCSEs: Maths - A*, Additional Maths - A*, Physics - A*, English Language - A*, English Literature - A*, Biology - A*, Chemistry - A*, French - A, History - A, RE - A, Art - B.\\

\end{tabularx}
%-------------------------------------
%	SCHOLARSHIPS AND ADDITIONAL INFO
%-------------------------------------
\section{Scholarships and Certificates}
\begin{tabularx}{\textwidth}{lX}

\textsc{Sept.} 2013 & Department of Mathematics Scholarship - awarded to the top 10 students who achieved the highest 'A' level grades of that year's intake.\\
\textsc{Dec.} 2013 & Department of Mathematics Prize - awarded to highest mark in class test for Computing for Mathematics module.\\
\textsc{Jan.} 2013 & Department of Mathematics Sponsored conference attendance - awarded for highest mark in individual research project during which I developed and implemented Markovian models.\\

\end{tabularx}
%--------------------
%	COMPUTER SKILLS
%--------------------
\section{Programming Skills}
I am proficient in most aspects of computing:

\begin{itemize}
    \item Operating Systems: Windows, MacOS, Linux (server and client);
    \item General software: Excel, Word Processing (\LaTeX\, Microsoft Word, Libre office), Presentation (Beamer, Microsoft Powerpoint);
    \item Programming: Python, Django, Sql, Ruby, C and well evidenced ability to gain proficiency in new languages quickly.
\end{itemize}

During my first year at University I gained proficiency in the web framework Django and developed a dynamic website: \url{http://thefightclub.herokuapp.com/}.
%-----------------------------
%	INTERESTS AND ACTIVITIES
%-----------------------------
\section{Acheivments and Interests}
I have been involved in Scouting from the age of 8, playing a \textbf{leading role} in the organisation both as member and a leader.
Recently, I was appointed a group-wide, adult leader position which will allow me to continue the work I have been doing whenever I am home from University. \\
\\
I have played Rugby Union from the age of 5, reaching County standard and playing for the Welsh Exiles before injury prevented me from carrying on.
This gave me a lot of experience of \textbf{working within a team}, both as a \textbf{captain} and a member. \\
\\
On starting at Cardiff University, I decided to take up a new sport in order to maintain my level of fitness.
During the course of the year, I've been promoted to the second team and have represented my university at several tournaments. \\
I have been \textbf{elected} to serve as treasurer for the next academic year once again demonstrating my \textbf{ability} and \textbf{recognition} to take on \textbf{responsibilities}.\\
\\
In my spare time I relax by playing the piano, having achieved Grade 5 some years ago. I hold a full, clean UK driving licence.
%-----------------
%	GRADE TABLES
%-----------------
\bigskip
\par{\centering\Large {\textsc{First Year Grades}}
\par}
%\large{\centering Grades\par}\normalsize

\begin{center}
\begin{tabular}{lcc}

\multicolumn{1}{c}{\textsc{Exam}} & \textsc{Credit}&\textsc{\%}\\ \hline
Analysis I & 10 & 78\\
Dynamical Systems and Chaos & 10 & 80\\
Calculus & 10 & 71\\
Algebra I & 10 & 62\\
Probability Theory & 10 & 81\\
\\
Algebra II & 10 & ?\\
Analysis II & 10 & ?\\
Elementry Differential Equations & 10 & ?\\
Statistical Inference & 10 & ?\\
Elementry Number Theory & 10 & ?\\
\\
Computing for Mathematics & 20 & 95\\
\cline{2-3}
&\textsc{Average}&?

\end{tabular}
\end{center}
\bigskip
%------------------------------------------------
\end{document}
