\documentclass[12pt]{letter}
\usepackage{parskip}
\usepackage{url}
\usepackage{multicol}
\usepackage[cm]{fullpage}
\usepackage{hyperref}
\usepackage{tabularx}

\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

\signature{James Campbell}
\address{97 Mackintosh Place \\ Cardiff \\ CF24 4RJ}
\longindentation=0pt

\begin{document}

\begin{letter}
{Lloyds Banking Group \\ Cardiff}
\opening{Dear Mr Millett,}

Re: Industrial Placement

I wish to apply for the role of Risk Analyst that was spoken about at Cardiff University and have attached my CV accordingly.

As a Maths student my degree has provided me with the perfect skills for this position.
In particular, it involves a great deal of problem solving skills combined with understanding complex and technical topics.
During a recent summer research placement I have shown that I am very self-motivated and able to communicate effectivley when working as part of a team.
The placement involved a large amount of programming and this is something I know I would have the chance to develop further with a placement at Lloyds.

I am a quick learner with keen interest in the financial sector and I would be very grateful for the opportunity to start my career with Lloyds.
You have provided many rewarding placements to Cardiff students in the past and I know how valuable the experience they gained will be in the future.


Thank you for taking the time to look at my applicaton, I look forward to hearing from you in the future.

\closing{Yours Faithfully,}


\end{letter}

\end{document}