\documentclass[a4paper]{article}

\usepackage{parskip}
\usepackage{url}
\usepackage{multicol}
\usepackage[margin=1.5cm]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{ltablex} % allows tabularx to extend over multiple pages

\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault}
\usepackage[T1]{fontenc}


\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{3pt}{3pt} % Spacing around sections

\begin{document}
\pagestyle{empty} % Removes page numbering
%---------------------------------
%	NAME AND CONTACT INFORMATION
%---------------------------------
\begin{multicols}{2}

\raggedright{\textsc{\Huge{James Campbell}}}\\
\columnbreak
\raggedleft{
+44 (0)7876 075714\\
\href{mailto:james.campbell@tanti.org.uk}{james.campbell@tanti.org.uk}\\
\href{http://www.jamescampbell.org.uk}{www.jamescampbell.org.uk}\\
\href{https://github.com/theref}{github.com/theref}}

\end{multicols}

%----------------------
%   PERSONAL PROFILE
%----------------------
%TODO - edit this section before sending it
\section{Personal Profile}
I am an undergraduate mathematics student on course to obtain a First Class Degree with honours, currently seeking a post graduate position in applied mathematics.
I have undertaken mathematical research throughout my undergraduate career, mainly focusing on the area of Game Theory, with a small contribution made to the area of Alternating Sign Matrices.
I also spent a year working at one of the UK's largest Insurance companies applying my analytical skills within an industrial environment.
\\
Since my first undergraduate year, I have been awarded a mathematics scholarship, presented my work at an international conference and twice been selected from 160 of my peers to undertake a research internship during the summer break.

%--------------------
%	WORK EXPERIENCE
%--------------------
\section{Work Experience, Research and Publications}
\begin{tabularx}{\textwidth}{lX}
%------------------------------------------------
\textsc{Sept. 2016 - } & Final Year Project, "Fingerprinting Prisoners Dilemma Strategies"\\
\textsc{May 2017} & \footnotesize{Reproduced research to differentiate between different strategies in Prisoners Dilemma using fingerprinting. Those tools where added to the open source library Axelrod-Python, and then used to analyse all of the strategies within the library. The second half of the project will be to develop novel ways to categorise and identify strategies. This improved my software development skills and also allowed to me to undertake a large amount of independent research with some guidance from my supervisor.}
\\
\\
%------------------------------------------------
\textsc{Autumn Semester} & Tutoring of 1\textsuperscript{st} Year Students Studying 'Computing for Mathematics'\\
\textsc{2016 \& 2014} & \footnotesize{Ran weekly lab sessions for 1\textsuperscript{st} year students learning python. This was a beginners course that covered all the basics of OO programming and also included a brief introduction to \LaTeX.}
\\
\\
%------------------------------------------------
\textsc{August} & Co-Author of "An Open Framework for the Reproducible Study of the Iterated Prisoner’s Dilemma" \\
\textsc{2016} & \footnotesize{The paper can be found at \url{http://openresearchsoftware.metajnl.com/articles/10.5334/jors.125/}}
\\
\\
%------------------------------------------------
\textsc{Sept. 2015 -} & Pricing Analyst at Admiral Group PLC \\
\textsc{July 2016} & \footnotesize{Obtained a prestigious industrial placement at one of the UK's largest Insurance companies. I worked in the Pricing Department, analysing claims statistics to make decisions about the underlying pricing structure that produces a quote for potential customers. For more information please visit \url{http://www.admiral.com/about-us/}}
\\
\\
%------------------------------------------------
\textsc{Summer} & Research Internship, Cardiff University School of Mathematics \\
\textsc{2015} & \footnotesize{Independently investigated "The expected wait in a tandem queue with blocking with a game theoretic study of the Hospital EMV interface" with guidance from Dr. Vince Knight. A paper has been started and should be finished sometime after my graduation.}
\\
\\
%------------------------------------------------
\textsc{Summer} & Research Internship, Cardiff University School of Mathematics \\
\textsc{2014} & \footnotesize{Employed for the Summer to lead a project developing Game Theoretic algorithms within the open source mathematics package, Sage.
Areas of Game Theory included: Normal Form Games, Co-operative Games and Matching Games. The code produced is available on several branches at \url{https://github.com/theref/sage-game-theory/}}
\\
\\
%------------------------------------------------
\textsc{Spring Semester} & Development of a Django Web Application\\
\textsc{2014} & \footnotesize{During an 11 week assessed activity of my Computing for Mathematics module, I developed a dynamic web application using the Django framework. The application can be viewed at \url{http://thefightclub.herokuapp.com} and the code is available at \url{https://github.com/Fight-Club/fightclub/}}
\\
\\
\end{tabularx}

%--------------
%	EDUCATION
%--------------
\section{Education}
\begin{tabularx}{\textwidth}{lX}
%------------------------------------------------
\textsc{Current} & \textsc BSc Mathematics and its Applications \\
&\normalsize Cardiff University, Department of Mathematics\\
& First Class Degree with Honours expected June 2017 \\
\\
%------------------------------------------------
\textsc{Sept. 2011 -} & St. Nicholas Catholic High School\\
\textsc{June 2013} & A-Levels: Maths - A*, Further Maths - A, Physics - A\\
& AS-Levels: Biology - B, Chemistry - B\\
\\
%------------------------------------------------
\textsc{Sept. 2006 -} & St. Nicholas Catholic High School\\
\textsc{June 2011} & GCSEs: Maths - A*, Additional Maths - A*, Physics - A*, English Language - A*, English Literature - A*, Biology - A*, Chemistry - A*, French - A, History - A, RE - A, Art - B.\\
\end{tabularx}

%-------------------------------------
%	SCHOLARSHIPS AND ADDITIONAL INFO
%-------------------------------------
\section{Scholarships and Prizes}
\begin{tabularx}{\textwidth}{lX}
%------------------------------------------------
\textsc{Mar.} 2015 & Sage Conference at UC Davis, California - Earned the opportunity to spend a week attending a conference dedicated to Sage held at UC Davis during which I contributed code related to Alternating Sign Matrices \url{https://wiki.sagemath.org/days64}.\\
\textsc{Jan.} 2014 & Django Conference - I was invited to talk at the UK's first ever Django conference where I presented the work I had completed for my computing coursework.\\
\textsc{Dec.} 2013 & Department of Mathematics Prize - awarded for the highest mark in Computing for Mathematics module.\\
\textsc{Sept.} 2013 & Department of Mathematics Scholarship - awarded to the top 10 students who achieved the highest 'A' level grades of that year's intake.\\
\end{tabularx}

%--------------------
%   VOLUNTEERING
%--------------------
\section{Volunteering}
\begin{tabularx}{\textwidth}{lX}
%------------------------------------------------
\textsc{Summer} & Designed and Built Playgrounds for Schools in Indonesia, CAUKIN \\
\textsc{2016} & \footnotesize{As a group of students we designed and built 2 playgrounds for schools in Indonesia. Everything was organised and managed by members of the team, with no external companies involved. This improved my project management skills and also developed my creativity. For more information please visit \url{http://www.caukinstudio.com}}
\\
\\
%------------------------------------------------
\textsc{Sept. 2013 -} & Adult Leader at 1\textsuperscript{st} Helsby Scouts\\
\textsc{Current} & \footnotesize{Continued to develop communication skills whilst helping to supervise and teach children aged 10 - 16 years.
Currently organising and managing a 2 week international expedition that will take place north of the Arctic circle in summer 2017, \url{http://nord2017.no/english/}}
\\
\\
%------------------------------------------------
\textsc{Sept. 2010 -} & Referee with the Rugby Football Union \\
\textsc{Sept. 2013} & \footnotesize{I began refereeing rugby union at the age of 15. Within 3 years, I had been promoted from level 15 to level 6 - the highest regional level and only one below the point where I could referee national level games.
The experience of taking charge of 30 men (often twice my age) in an aggressive and physical sport has given me confidence in my ability to remain calm in high pressure situations.}
\\
\\
%------------------------------------------------
\textsc{Sept. 2009 -} & Young Leader at 1\textsuperscript{st} Helsby Scouts\\
\textsc{July 2013} & \footnotesize{Developed communication skills whilst helping to supervise and teach children aged 6 - 10 years.
I was regularly assigned to lead small group activities which improved my organisation and leadership skills.}\\
\end{tabularx}

%--------------------
%	COMPUTER SKILLS
%--------------------
\section{Programming Skills}
I am proficient in most aspects of computing:

\begin{itemize}
    \item Operating Systems: Windows, MacOS, Linux (server and client);
    \item General software: Excel, Word Processing (\LaTeX, Microsoft Word, Libre office), Presentation (Beamer, Microsoft Powerpoint);
    \item Programming: Python, Django, Ruby, Git, Trac and well evidenced ability to gain proficiency in new languages quickly.
    \item Supercomputing: Experience using Cardiff University's supercomputer \href{http://www.cardiff.ac.uk/advanced-research-computing}{RAVEN} and submitting jobs using PBS.
\end{itemize}

For an overview of my programming portfolio, please see my Github profile: \url{https://github.com/theref}.

%-----------------------------
%	INTERESTS AND ACTIVITIES
%-----------------------------
\section{Achievements and Interests}
I have been involved in Scouting from the age of 8, playing a leading role in the organisation both as member and a leader.
Recently, I was appointed a group-wide, adult leader position which will allow me to continue the work I have been doing whenever I am home from University.
I will be leading a group of 30 scouts on an international expedition in Norway in summer 2017.\\
\\
I have played Rugby Union from the age of 5, reaching county standard and playing for the Welsh Exiles before injury forced my retirement.
This gave me a lot of experience of working within a team, both as a captain and a member. \\
\\
At University, I took up the sport of Ultimate Frisbee. I have been promoted to the first team, represented my university at several national tournaments (including varsity) and was elected to serve as treasurer during my second year. \\
\\
In my spare time I relax by playing the piano, having achieved Grade 5 some years ago. I hold a full, clean UK driving licence.

%-------------
%   REFEREES
%-------------
\section{Referees}

\begin{minipage}[b]{0.5\linewidth}
Dr. Vince Knight\\
School of Mathematics\\
Cardiff University\\
Senghennydd Road\\
CARDIFF, Wales, UK.\\
CF24 4AG\\
knightva@cardiff.ac.uk
\end{minipage}
%
%
\begin{minipage}[b]{0.5\linewidth}
Prof. Nikolai Leonenko\\
School of Mathematics\\
Cardiff University\\
Senghennydd Road\\
CARDIFF, Wales, UK.\\
CF24 4AG\\
leonenkon@cardiff.ac.uk
\end{minipage}

%-----------------
%	GRADE TABLES
%-----------------
% \bigskip
% \par{\centering\Large {\textsc{First Year Grades}}
% \par}
%\large{\centering Grades\par}\normalsize

% \begin{center}
% \begin{tabular}{lcc}

% \multicolumn{1}{c}{\textsc{Exam}} & \textsc{Credit}&\textsc{\%}\\ \hline
% Analysis I & 10 & 78\\
% Dynamical Systems and Chaos & 10 & 80\\
% Calculus & 10 & 71\\
% Algebra I & 10 & 62\\
% Probability Theory & 10 & 81\\
% \\
% Algebra II & 10 & 72\\
% Analysis II & 10 & 71\\
% Elementry Differential Equations & 10 & 79\\
% Statistical Inference & 10 & 58\\
% Elementry Number Theory & 10 & 72\\
% \\
% Computing for Mathematics & 20 & 96\\
% \cline{2-3}
% &\textsc{Average}&76.3

% \end{tabular}
% \end{center}


%------------------------------------------------
\end{document}
